A Review of the Movie \textit{Apocalypse Now}

### 2015-11-16 paper.tex
Removed contractions

While hiding out from Kilgore's search parties under the low overhang of trees, Chef and Willard decide to wander into the jungle in search of mango's. After a short walk and discussing the origin of Chef's name, Willard hears rustling and becomes extremely alert. He pulls back some large brush, only to reveal a tiger, which attacks. The two scramble back to the boat, screaming hysterically and forcing Clean to unload the machine gun. When they finally get back on the boat and explain what happened, Chef starts to curse and swear that he is done with the war, demanding to leave. However, he is calmed down while Chief starts the boat and continues on.

>>>>

While hiding out from Kilgore's search parties under the low overhang of trees, Chef and Willard decide to wander into the jungle in search of mangoes. After a short walk and discussing the origin of Chef's name, Willard hears rustling and becomes extremely alert. He pulls back some large brush, only to reveal a tiger, which attacks. The two scramble back to the boat, screaming hysterically and forcing Clean to unload the machine gun. When they finally get back on the boat and explain what happened, Chef starts to curse and swear that he is done with the war, demanding to leave. However, he is calmed down while Chief starts the boat and continues on.
